Using Nature Inspired Algorithms for Feature Selection in Transaction Fraud Detection

### 2020-05-31 paper/main.tex
Update conclusion

In our experiments, we found out Grey Wolf Optimizer as the best nature-inspired algorithm for feature selection. It achieved significantly better results than other nature-inspired algorithms and better results that recursive feature elimination.

>>>>

In our experiments, we found out Grey Wolf Optimizer as the best nature-inspired algorithm for feature selection. It achieved significantly better results than other nature-inspired algorithms and better results (1.4\% ROC AUC) that recursive feature elimination, while using by half fewer features.
